The Way Forward in Parallelizing Dynamic Languages

### 2014-05-02 talk/icooolps2014/position-paper.tex
add some text

Unfortunately, STM has a big performance problem. One way to approach
this problem is to make STM systems that make better use of low-level
features in existing OS kernels.
We are currently working on a STM system that makes use of
several such features like virtual memory and memory segmentation.
We further tailor the system to the discussed use case which gives us
an advantage over other STM systems that are more general. With this
approach, initial results suggest that we can keep the overhead of STM
below 50\%. A hybrid TM system, which also uses HTM to accelerate
certain tasks, looks like a very promising direction of research
too. In general we believe that further work to reduce the overhead of
STM is very worthwhile.

>>>>

Unfortunately, STM has a big performance problem. Particularly, for
our use case there is not much static information available since we
are executing a program only known at runtime. Additionally, replacing
the GIL means running everything in transactions, so there is not much
code that can run outside and be optimized better.

One way to get more performance is to make STM systems that make
better use of low-level features in existing OS kernels.  We are
currently working on a STM system that makes use of several such
features like virtual memory and memory segmentation.  We further
tailor the system to the discussed use case which gives us an
advantage over other STM systems that are more general. With this
approach, initial results suggest that we can keep the overhead of STM
below 50\%. A hybrid TM system, which also uses HTM to accelerate
certain tasks, looks like a very promising direction of research
too. In general we believe that further work to reduce the overhead of
STM is very worthwhile.
